R for Clinical Study Reports and Submission

### 2022-03-18 submission-package.Rmd
fix some minor issues
Capture `pack()` output using asciicast

In eCTD deliverable, the analysis dataset and source code are saved
under the eCTD module 5 (clinical study reports) folder

@@

>>>>

In eCTD deliverable, the analysis datasets and source code are saved
under the eCTD module 5 (clinical study reports) folder

@@

```{r, echo=FALSE, eval=FALSE}
# Generated this asciicast SVG by running
rmarkdown::render("images/pack.Rmd")

patch_asciicast_theme <- function(x) {
  x <- gsub("rgb\\(40,45,53\\)", replacement = "rgb\\(255,255,255\\)", x = x)
  x <- gsub("rgb\\(185,192,203\\)", replacement = "rgb\\(0,0,0\\)", x = x)
  x <- gsub("rgb\\(113,190,242\\)", replacement = "rgb\\(52,101,164\\)", x = x)
  x <- gsub("rgb\\(168,204,140\\)", replacement = "rgb\\(78,154,6\\)", x = x)
  x <- gsub("rgb\\(102,194,205\\)", replacement = "rgb\\(6,152,154\\)", x = x)
  x
}

readLines("images/images/pack.svg", warn = FALSE) |>
  patch_asciicast_theme() |>
  writeLines(con = "images/images/pack.svg")

# For best web browser compatibility:
# Open pack.svg in web browser, print as PDF
# pdfcrop pack.pdf
# convert -density 300 pack-crop.pdf pack.png
```
